% LaTeX file for resume
% This file uses the resume document class (res.cls)
\documentclass[margin]{res}

% the margin option causes section titles to appear to the left of body text
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{hyperref}
\hypersetup{
    colorlinks = true,
    allcolors = {blue}
}

\begin{document}

% Center the name over the entire width of resume:
\moveleft.5\hoffset\centerline{\large\bf Cody Scott}
% Website Link
\moveleft.5\hoffset\centerline{\url{http://siecje.github.io/}}

% address begins here
% Again, the address lines must be centered over entire width of resume:
\moveleft.5\hoffset\centerline{cody.j.b.scott@gmail.com}

% Draw a horizontal line the whole width of resume:
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

\begin{resume}

\section{Education}
\textbf{\textsl{Honours Bachelor of Science, Computer Science}} \hfill Sept. 2010 - Apr. 2015 \\
\href{https://www.lakeheadu.ca/}{Lakehead University}

\section{Work Experience}

\href{https://www.giatecscientific.com/}{Giatec Scientific Inc.} \\
\textbf{\textsl{Lead Software Developer}} \hfill Jan 2022 - Present \\
\textbf{\textsl{Manager of Software Development}} \hfill Feb 2020 - Jan 2022 \\
\textbf{\textsl{Senior Web Developer}} \hfill Jan 2019 - Feb 2020 \\
 \begin{itemize} \itemsep -2pt  % reduce space between items
  \item Infrastructure
  \begin{itemize} \itemsep -2pt  % reduce space between items
    \item Kubernetes, helm, Docker
    \item Microsoft Azure Cloud
    \item Linux signed boot, disk encryption
    \item Mulitple boot partitions
  \end{itemize}
 \item Backend
  \begin{itemize} \itemsep -2pt  % reduce space between items
    \item Python, NodeJS
    \item Django, Express, Flask
    \item REST, GraphQL
    \item PostgreSQL
  \end{itemize}
 \item Frontend (Giatec 360, SmartMix)
   \begin{itemize} \itemsep -2pt
     \item TypeScript
     \item Angular, React
     \item Cypress
   \end{itemize}
 \end{itemize}

\textsl{Perspexis Technologies Inc.} \\
\textbf{\textsl{Programmer (Employee \#2)}} \hfill July 2015 - Dec 2018 \\
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Backend
 \begin{itemize} \itemsep -2pt  % reduce space between items
  \item Python
  \item RPC, Custom TCP protocol
  \item Flask, XMLRPC, REST
  \item Linux, Postgres, Beanstalkd, Redis
  \item Jenkins
 \end{itemize}
 \item Frontend
   \begin{itemize} \itemsep -2pt
     \item Python
     \item PyQt5, Qt QML
     \item Webix JavaScript Framework
   \end{itemize}
 \end{itemize}

 \textsl{Golden Spear} \\
 \textbf{\textsl{Backend Developer (Contract)}} \hfill June 2015 \\
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Node.js application for online store
  \begin{itemize} \itemsep -2pt  % reduce space between items
   \item PhantomJS to scrape online stores
   \item Worked with Captain Crunch (John Draper)
  \end{itemize}
 \end{itemize}

\href{https://windriver.com/}{Wind River Systems} \\
\textbf{\textsl{Full Stack Developer}} \hfill Jan. 2013 - May 2015 \\

 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Created Internal and Customer Facing Websites
 \begin{itemize} \itemsep -2pt  % reduce space between items
  \item Python, Django, Flask
  \item JavaScript, NodeJS, AngularJS
 \end{itemize}
 \item Administered Linux Servers
   \begin{itemize} \itemsep -2pt
     \item SSH, Email, LDAP
     \item Databases (MySQL, SQLite, PostgreSQL, MongoDB)
   \end{itemize}
 \end{itemize}

\section{Technical Skills}
\textbf{\textsl{Languages:}}
\begin{itemize}
\renewcommand\labelitemi{--}
\item Python, JavaScript, Bash
\end{itemize}
\textbf{\textsl{Technologies:}}
\begin{itemize}
\renewcommand\labelitemi{--}
\item \href{https://www.postgresql.org/}{PostgreSQL}
\item \href{https://nodejs.org/en}{NodeJS}
\item \href{https://www.djangoproject.com/}{Django}, \href{https://flask.palletsprojects.com/}{Flask}
\item \href{https://git-scm.com/}{git}, \href{https://www.mercurial-scm.org/}{Mercurial}
\item Linux
\item Kubernetes, Docker
\item \href{https://angular.io/}{Angular}
\end{itemize}

\section{Open Source}

\href{https://github.com/Siecje/heatpump-cost}{heatpump-cost} - Compare costs of a heat pump to other heating sources.

\href{https://github.com/Siecje/nginx-auth-proxy}{nginx-auth-proxy} - Authentication for multiple services using nginx.

\href{https://github.com/Siecje/qml-explorer}{qml-explorer} - A Debug Console for Qt QML.

\href{https://github.com/Siecje/loud-clips}{loud-clips} - Create a highlight reel of the loud parts of a video.

\href{https://github.com/Siecje/htmd}{htmd} - Write Markdown and Jinja2 templates to create a website.

\href{https://github.com/Siecje/hashword}{hashword} - Password Manager.

\end{resume}
\end{document}
